SFJ: An implementation of Semantic Featherweight Java

### 2020-04-24 conference/camera ready/paper.tex
more on polygons

\subsection{Type System for SFJ}

@@

Thus, if we pass to \emph{diagonal} an argument of type \emph{Triangle}, we get a typechecking error at compile time, as illustrated in the accompanying video \cite{UD20}.

>>>>

\subsection{Type System for SFJ}
\label{sec:typing}

@@

If we write in our SFJ program the following expression:
$$
    (\textbf{new}\ Diagonal()).diagonal(\textbf{new}\ Square())
$$
the argument \textbf{new} $Square()$ of the $diagonal$ method is of type $Square$, by the type system in \autoref{sec:typing} and $Square$ is contained in the set of the parameter type of the method, so this expression will successfully type checks.

However, if we write the following SFJ expression:
$$
    (\textbf{new}\ Diagonal()).diagonal(\textbf{new}\ Triangle())
$$
Type $Triangle$ is not contained in $\left\{Polygon, Square, Rhombus \right\}$, therefore this expression will not type check and will return a type error at compile time.

This is further illustrated in the accompanying video of this paper \cite{UD20}.
